Manuscript title here

### 2021-01-05 docs/ms/ms.RMD
updated and filxed issue with cbind.fill recognition with Roxygen

# Introduction

Increasing global temperatures are altering the diversity, structure, and functioning of Earth's ecosystems [@Brose2012][@walther2002][@Woodward_Dybkjær_Ólafsson_eta2010]. The effects of this warming manifest through shifting species ranges [],

The provision and maintenance of ecosystem functions are underpinned by the network of species interactions across which energy, materials, and information are exchanged [@deRuiter1995][@thompson2012]. Specifically, warming can directly alter , is tied to the magnitudes and relative distributions of energy fluxes among species and trophic levels [@may1972][@barnes2018].

Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (~5 - 28$^\circ$C). Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011][@padfield2017] and within streams seasonally [@gorman2012][@hood2018]. The dynamics of basal resource supply has a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to consumer to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams. Further, we predicted that food web OM fluxes will 'speed up' with increasing temperature through increases in the importance of relatively faster, higher turnover consumers. Within streams, the speeding up of ecosystems will lead to earlier food web fluxes in warmer compared to colder streams.

>>>>

# Introduction
<!--- warming and effects in food webs --->
Increasing global temperatures are altering the diversity, structure, and functioning of Earth's ecosystems [@brose2012][@walther2002][]. While a growing body of theoretical and empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [][][], general patterns are uncertain and empirical studies often idiosyncratic, especially at higher levels of organizations such as communities and food webs [@walter2012][@woodward2010]. This uncertainty arises because the influence of environmental temperature on ecosystems occurs through complex direct and indirect pathways, such as shifting species ranges [][] and subsequent changes to local and regional communities [], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004][@arrhenius18]. Identifying general effects of temperature is further complicated by the fact that natural variation in temperature often exists concurrently with other environmental gradients (e.g., light, water, and/or nutrient availability). Understanding the effects of temperature...alterations to ecosystem function and the services they provide. 
<!--- Speeding up of food web: Species levels--->
The provision and maintenance of ecosystem functions are underpinned by the network of species interactions across which energy, materials, and information are exchanged (e.g., food webs; [@deruiter1995][@thompson2012]. Characteristics The magnitude The response of ecosystem function to environmental drivers and variability <!---Ecosystem functionality---> is tied to the magnitudes and relative distributions of energy fluxes among species and trophic levels [@may1972][@barnes2018]. The complexity in responses to warming arise from 
<!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (~5 - 28$^\circ$C). Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011][@padfield2017] and within streams seasonally [@gorman2012][@hood2018]. The dynamics of basal resource supply has a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to consumer to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams. Further, we predicted that food web OM fluxes will 'speed up' with increasing temperature through increases in the importance of relatively faster, higher turnover consumers. Within streams, the speeding up of ecosystems will lead to earlier food web fluxes in warmer compared to colder streams.
